Compact linkable ring signatures and applications

### 2019-06-03 paper/mrl.tex
Both versions of paper (MRL and IACR)

\documentclass{article}

\usepackage{enumerate}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}

@@

\title{Compact linkable ring signatures and applications}
\author[1]{Brandon Goodell}
\author[1]{Sarang Noether}
\author[2]{\texttt{RandomRun}}
\affil[1]{Monero Research Lab, \texttt{\{surae,sarang\}@getmonero.org}}
\affil[2]{Independent researcher}
\date{}

\begin{document}
\maketitle

>>>>

\documentclass{mrl}

\usepackage{enumerate}
\usepackage[utf8]{inputenc}

@@

\title{Compact linkable ring signatures and applications}
\authors{Brandon Goodell\footnote{\texttt{surae.noether@protonmail.com}} and Sarang Noether\footnote{\texttt{sarang.noether@protonmail.com}} and \texttt{RandomRun}}
\affiliations{Monero Research Lab}
\date{\today}
\type{RESEARCH BULLETIN}
\ident{MRL-0011}

\begin{document}
